Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-02-06 paper.tex
add OCR robustness section from old paper

>>>>

We use the widely-used open-source Tesseract 2 engine and first compiled 15 ground-truth, noise-free document images from a new corpus of born-digital documents, whose ground-truth strings are known. We then used Tesseract to generate OCR predictions on these noise-free documents, as a baseline for comparison. We considered these OCR predictions as the ground-truth labels for each document. Next, we generated noisy versions of the 15 documents by running them through an Augraphy pipeline, and again used Tesseract to generate OCR predictions on these noisy documents. We compared the word accuracy rate on the noisy OCR results versus the ground-truth noise-free OCR results, and found that the noisy OCR results were on average 52\% less accurate, with a range of up to 84\%. This example use-case demonstrates the effectiveness of using Augraphy to create challenging test data for evaluating OCR systems.
